Approximation as Differentiation notes

### 2025-02-10 notes.tex
Signatures.
acmsmall.

\documentclass[nonacm]{acmart}

@@

Some notes on the key constructions:
\begin{itemize}
\item Category of families $\Fam$
\item Category of bounded lattices and Galois connections
\end{itemize}

\noindent $\Set$ will often be $\Setoid$ in the Agda code but I'm glossing that here.

@@

\noindent Equivalently, $\Fam(I,C)$ is the functor category $\FunCat{I}{C}$.

@@

@@

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\end{itemize}
\note{Ignoring lists for now.}

>>>>

\documentclass[acmsmall,nonacm]{acmart}

%\geometry{paperwidth=8.3in, paperheight=11.7in}

@@

Some of the key constructions:
\begin{itemize}
\item Category of families $\Fam$
\item Category of $\LatGal$ of bounded lattices and Galois connections
\end{itemize}

\noindent $\Set$ will often be $\Setoid$ in the Agda implementation but will gloss that here.

@@

\noindent Equivalently $\Fam(I,C)$ is the functor category $\FunCat{I}{C}$ where we interpret $I$ as a
discrete category.

@@

\section{Language}

\subsection{Syntax}

We parameterise our language over a signature $\Sigma = (S, \phi, R)$ consisting of:
\begin{itemize}
\item a set $S$ of sorts
\item a set of operations $\phi$ with signature $\Sigma(\phi) \in S^* \times S$
\item a set of relations $R$ with signature $\Sigma(R) \in S^*$
\end{itemize}

@@

We interpret our language into any category with:
\begin{itemize}
\item finite products (binary products and a terminal object)
\item Booleans
\end{itemize}
\note{Ignoring lists for now; Booleans can be derived from coproducts.}
